### 2019-02-21 sections/introduction.tex
small bit on mtasks

\ITASKS is an implementation of \TOP, in the form of a shallowly embedded domain-specific language in the lazy functional programming language Clean.
It is a library that provides editors, monadic combinators, and shared data sources.
\ITASKS uses the generic programming facilities of Clean to derive rich client and server applications from a single source.
It has been used to model an incident management tool for the Dutch coast guard~\cite{conf/iscram/LijnseJP12}.
Also it has been used numerous times to prototype ideas for Command and Control~\cite{theses/nlda/Kool17, theses/radboud/Stutterheim17}, and in a case study for the Dutch tax authority \cite{conf/sfp/StutterheimAP17}.

\MTASKS is a subset of \ITASKS,
focussing on \IOT devices and deployment on micro controllers.
\fixme{Add examples.}

\fixme{Say what lacks in these approaches: no formal reasoning about properties.}

@@

  \item
    Along with the semantics, we present the following semantic observations on tasks:
    the current value, whether a term is stuck, the current user interface, and the accepted inputs. \fixme{we do not provide observation for user interface!}

>>>>

\ITASKS is an implementation of \TOP, in the form of a shallowly embedded domain-specific language in the lazy functional programming language Clean.
It is a library that provides editors, monadic combinators, and shared data sources.
\ITASKS uses the generic programming facilities of Clean to derive rich client and server applications from a single source.
It has been used to model an incident management tool for the Dutch coast guard~\cite{conf/iscram/LijnseJP12}.
Also it has been used numerous times to prototype ideas for Command and Control~\cite{theses/nlda/Kool17, theses/radboud/Stutterheim17}, and in a case study for the Dutch tax authority~\cite{conf/sfp/StutterheimAP17}.

\MTASKS is a subset of \ITASKS,
focussing on \IOT devices and deployment on micro controllers.
It has been used to control home thermostats and other home automation applications \fixme{cite}.

Both implementations currently lack formal semantics which can be used to prove properties about tasks.

@@

  \item
    Along with the semantics, we present the following semantic observations on tasks:
    the current value, whether a term is stuck, the current user interface, and the accepted inputs.
